Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v2.0/sections/7_conclusions.tex
Correct spellings

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adapted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices. As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nano transistors, enhancing their performance and inventing novel appliances.

>>>>

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adapted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices. As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nanotransistors, enhancing their performance and inventing novel appliances.

### 2021-08-16 paper/v2.0/sections/appendix_a.tex
Correct spellings

The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq. \ref{eq_1}) is quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimensional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right].
\end{equation}
Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can be presented by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}. We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
\end{equation}
This leads to
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Subsequenty, we can restrict $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that simply our previous expression as
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Here
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well-known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~\text{for}~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).

>>>>

The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq. \ref{eq_1}) is quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimensional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right].
\end{equation}
Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can be presented by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}. We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
\end{equation}
This leads to
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Subsequently, we can restrict $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that simply our previous expression as
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Here
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well-known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~\text{for}~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).
